\documentclass[../main.tex]{subfiles}
\graphicspath{{\subfix{../src/}}}


\begin{document}
\section*{Abstract}

% Introduction of problem
The human upper-limbs are some of the most important appendages of the human body.
The upper limbs of a human allows for interaction and manipulation of the environment, and acts as a crucial part of a functioning human body.
% Why we need to solve this problem
The loss of an upper limb, either congenital or traumatic severely reduces a person's ability to interact with- and perform simple day-to-day tasks
%in the environment
required for basic human living.
% Introduction to existing solutions and their flaws
This is a major problem for amputees, and can only be partially solved by rehabilitation using a prosthetic device, designed to provide a interface between a mechanical or robotic appendage, and the remaining appendage section of the amputee.
These prosthetic devices often only allow for a small degree of control through a limited interface at the attachment point of the prosthetic.
This often causes the amputee to neglect the rehabilitation and usage of the prosthetic, by choosing to reserve it for limited use, or reject it all together.
Amputees not choosing to make use of a prosthetic device, often cause overuse of their remaining limbs.
% This thesis researches.... Intro to my work
This thesis aims to decrease the gap between existing prosthetic devices and their real-life counterparts, with the purpose of increasing dynamic control and reduce the amount of manual manipulation from the amputee.
Doing so, hopefully decreases the amount of amputees choosing to reject their prosthetic device. 
Different control methods for prosthetic devices is researched, with a focus on processing and interpreting surface-electromyography data recorded from the upper appendage and the upper body.
% This thesis proposes... outcome of my work
The different control methods compared are variations of different methods in Machine Learning and Artificial Intelligence, with the purpose of creating a model suitable for classification or regression in order to convert muscle recordings into a controllable output for a prosthetic device.
This thesis proposes the use of feature-based Linear Discriminant Analysis for intent classification, and the usage of a 4-layer Recurrent Neural Network to predict the joint movements of the hand.
A method of creating a state of the art training dataset is explored, this dataset is proposed to be created with the Motive motion capture system, in cooperation with the Delsys Trigno muscle recording system and a custom made motion capture recording glove for the
%joint movements of the
hand.
Lastly, an anatomically correct simulated prosthetic hand is proposed, with the purpose of visualizing and testing implemented prosthetic device controllers.
The implemented classification method achieves an 3-way classification accuracy of $61\%$.
Furthermore, the implemented regression method has an average error of $0.1$ radians.

%TODO: Should i have results in here?

\end{document}
