\documentclass[../main.tex]{subfiles}
\graphicspath{{\subfix{../src/}}}


\begin{document}

\section*{Acknowlegdements}

This thesis is written by Thomas Alexgaard Jensen (tjens18@student.sdu.dk), a master's degree robotics engineering student at the University of Southern Denmark (SDU), in the period July 2022 to May 2023.
% Double Check dates
This thesis is written under the supervision of Poramate Manoonpong (poma@mmmi.sdu.dk) \& Xiaofeng Xiong (xizi@mmmi.sdu.dk) as part of SDU Biorobotics.
I would like to thank my supervisors Poramate Manoonpong \& Xiaofeng Xiong for granting access to Biorobotics Lab, and the usage of the Motive Motion Capture system in combination with the Delsys Trigno muscle recording system.
I would like to thank Poramate Manoonpong \& Xiaofeng Xiong for helping me realize my passion project of researching methods of developing prosthetic devices.
Lastly, I would like to thank Poramate Manoonpong \& Xiaofeng Xiong for providing meetings, help and relevant research papers during the development of this thesis.

I would like to thank my fellow student Kristian Varming for providing help with the usage of the Motive Motion Capture system.
I would like to thank my fellow students Erik Lindby, Mikkel Werge Olsen \& Claus Huynh for continuous conversations about development goals and directions that greatly helped the direction and development of this thesis.
I would like to thank my friend Frederik Tørnstrøm, for providing motivational support and development conversations during the development of the thesis.
Lastly, i would like to thank my family for providing motivational support when it was needed the most.
% Thanks to Poramate \& Xiaofeng for coppeliasim recommendation

\end{document}
